models with mice

### 2024-03-13 withmice.Rmd
making pretty Lm tables

---
title: "models with mice"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

```{r}

@@

formice <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext"))

@@

formice <- formice %>%
  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
  mutate(across(State, ~factor(.x, ordered = FALSE)))

str(formice)
summary(formice)

@@

## Mifa for Kahan scale 
```{r, echo =FALSE}
library(mifa)
library(mice)
library(psych)

 #cov_vars = -c(State, Risky_Solar, Risky_Nuclear, Risky_Coal, Ben_Solar, Ben_Nuclear, Ben_Coal, DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE, ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB, OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION, DISPLACESOLAR, POLLUTESOLAR, HEALTHSOLAR, JOBSSOLAR, BEAUTYSOLAR, PRIDESOLAR, NPRIDESOLAR, DEVSOLAR, PROSPERSOLAR, RELYSOLAR, DISPLACECOAL, POLLUTECOAL, HEALTHCOAL, JOBSCOAL, BEAUTYCOAL, PRIDECOAL, NPRIDECOAL, DEVCOAL, PROSPERCOAL, RELYCOAL, DISPLACENUCLEAR, POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR, PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR, RELYNUCLEAR, age, urban_rural, gender, caste, religion),

kahanall <- codedmodule2 %>%
          dplyr::select(c(starts_with("K_")))

mikahan <- mifa(data= kahanall,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 427,)

@@

@@

#checking imputations: Kahan scale

```{r}

orgscores <- data.frame(kahanefascores)

summary(mikahan)
names(mikahan)

@@

## Distribution check: kahan Scale

```{r}
# Add an identifier column to each dataset
fct_scores$Dataset <- 'fct_scores'
orgscores$Dataset <- 'orgscores'

# Combine the datasets for plotting
combined_data <- rbind(fct_scores, orgscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
combined_data <- combined_data[, c("MR1", "MR2", "Dataset")]

ggplot(combined_data, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR1 for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

```
```{r}
ggplot(combined_data, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of MR2 for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  scale_color_manual(values = c("fct_scores" = "blue", "orgscores" = "red")) +
  theme_minimal()

@@

# Mifa for new eco-pol value scale : Nuclear energy

```{r}

ecopoln <- codedmodule2[, grep("NUCLEAR|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]

miecopol <- mifa(data= ecopoln,
                cov_vars = everything(),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

fit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(fit2, sort= TRUE, cut= 0.4)

@@

fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:23], fit2)$scores)

@@

## Checking imputations : Eco-pol scale

@@

```{r}

nscores <- data.frame(ecopolall_scores$scores)
nscores

# Add an identifier column to each dataset
fct_scores2$Dataset <- 'imputed'
nscores$Dataset <- 'original'

# Combine the datasets for plotting
compare2 <- rbind(fct_scores2, nscores)

# Select only necessary columns (assuming 'Index' isn't needed anymore)
compare2<- compare2[, c("MR1", "MR2", "Dataset")]

ggplot(compare2, aes(x = Dataset, y = MR1, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Pdevelop for Each Dataset", x = "", y = "MR1 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

@@

```{r}

ggplot(compare2, aes(x = Dataset, y = MR2, fill = Dataset)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, aes(color = Dataset), size = 1.5, alpha = 0.5) +
  labs(title = "Boxplot of Ndevelop for Each Dataset with Points", x = "", y = "MR2 Value") +
  scale_fill_manual(values = c("imputed" = "blue", "original" = "red")) +
  scale_color_manual(values = c("imputed" = "blue", "original" = "red")) +
  theme_minimal()

@@

```{r}

@@

>>>>

---
title: "models with mice"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    keep_tex: yes
  keep_md: yes
---

@@

# Can do something with accept, reject and reluctantly accept.

@@

formice1 <- codedmodule2[, grep("State|age|urban_rural|gender|caste|religion|Solar|SOLAR|Nuclear|NUCLEAR|Coal|COAL|K_S|K_E|K_H|K_I|WEALTHLIM|MECHANISATION|DECISIONDECEN|INDUSTRYSMALL|ECONOMYLOCAL|ENVOVERDEV|DEVOVERENV|OWNERPUB|OWNERREG|DECISIONCEN|INDUSTRYLARGE|ECONOMYGLOBAL|OWNERPVT|OWNERNOREG", names(codedmodule2))]%>%
        dplyr::select(-c("Language", "Risky_INDSolar", "Ben_INDSolar", "religiontext")) %>%
          mutate(across(age, ~factor(.x, ordered = TRUE)))%>%  
          mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
          mutate(across(State, ~factor(.x, ordered = FALSE))) %>%
          mutate(Uppercaste = ifelse(caste %in% c('Brahmin', 'General'), 1, 0)) %>%
          mutate(Male = ifelse(gender == 'Male', 1, 0))%>%
          mutate(Hindu = ifelse(religion == 'Hinduism', 1, 0))%>%
           mutate(Age = case_when(
                                  age == "18-24 years old" ~ 1,
                                  age == "25-34 years old" ~ 2,
                                  age == "35-44 years old" ~ 3,
                                  age == "45-54 years old" ~ 4,
                                  age == "55-64 years old" ~ 5,
                                  age == "65-74 years old" ~ 6,
                                  age == "75 years or older" ~ 7))

@@

formice <- formice1 %>%
  mutate(across(Risky_Solar:age, ~factor(.x, ordered = TRUE)))%>%
  mutate(across(urban_rural:religion, ~factor(.x, ordered = FALSE)))%>%
  mutate(across(State, ~factor(.x, ordered = FALSE)))

#str(formice)
summary(formice)

# litte's MCAR test

mcar_test(data= codedmodule2)

# p value = 1, which means MAR condition is met.

@@

# Kahan scale: MAR condition and missing data pattern 
```{r, echo=FALSE}

kahanall <- codedmodule2 %>%
          dplyr::select(c(starts_with("K_"), "age", "gender", "caste", "State", "urban_rural", "religion")) %>%
          mutate(across(gender:religion, ~factor(.x, ordered = FALSE))) %>%
          mutate(across(age, ~factor(.x, ordered = TRUE)))

str(kahanall)

md.pattern(kahanall) #the variables with missing values: K_SHARM K_IPROTECT K_IPRIVACY K_SPROTECT K_SLIMCHOI K_IINTRFER K_HEQUAL K_HREVDIS1

mcar_test(data=kahanall) # p values is less than 0.05 - the condition for MCAR is not met

# dataset with missing variables to compare and test group comaprisons

MARkahan <- codedmodule2 %>%
          dplyr::select(c("K_SHARM", "K_IPROTECT", "K_IPRIVACY", "K_SPROTECT", "K_SLIMCHOI", "K_IINTRFER",  "K_HEQUAL", "K_HREVDIS1" , "age", "gender", "caste", "State", "urban_rural", "religion"))

MARkahan$K_SHARM_MAR <- MARkahan$K_SHARM

MARkahan$K_IPROTECT_MAR <- MARkahan$K_IPROTECT

MARkahan$K_SPROTECT_MAR <- MARkahan$K_SPROTECT

MARkahan$K_SLIMCHOI_MAR <- MARkahan$K_SLIMCHOI

library(finalfit)

# "K_SHARM" = "(C)Sometimes the government needs to make laws that keep people from hurting themselves.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SHARM_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SHARM variable.")

#   "K_IPROTECT" = "(I)It’s not the government’s business to try to protect people from themselves."
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_IPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_IPROTECT variable.")

#  "K_SPROTECT" = "(C)The government should do more to advance society’s goals, even if that means limiting the freedom and choices of individuals.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SPROTECT_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

#  "K_SLIMCHOI" = "(C)The government should put limits on the choices individuals can make so they don’t get in the way of what’s good for society.",
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "K_SLIMCHOI_MAR"
MARkahan %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the K_SPROTECT variable.")

## Mifa for Kahan scale 
```{r, echo =FALSE}

library(mifa)
library(mice)
library(psych)

mikahan <- mifa(data= kahanall,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m = 50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 427,)

@@

## checking merging of imputations  : kahan scale

kahan_imp <- mice(kahanall, m =5, maxit =30,  seed = 427, print = FALSE)

kahan_imp$chainMean

#Kahan Factor scores: mean across all imputations

kahanallscores <- mice::complete(mice::mice(kahanall, m = 5, seed = 427, print = FALSE), "broad")

kahanallscores <- kahanallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

str(kahanallscores)

nkahanall <- kahanallscores %>%
  rowwise() %>%
  mutate( K_EWEALTH_mean = mean(c_across(starts_with("K_EWEALTH"))),
    K_IINTRFER_mean = mean(c_across(starts_with("K_IINTRFER"))),
    K_IPRIVACY_mean = mean(c_across(starts_with("K_IPRIVACY"))),
    K_SHARM_mean = mean(c_across(starts_with("K_SHARM"))),
    K_IPROTECT_mean = mean(c_across(starts_with("K_IPROTECT"))),
    K_SLIMCHOI_mean = mean(c_across(starts_with("K_SLIMCHOI"))),
    K_SPROTECT_mean = mean(c_across(starts_with("K_SPROTECT"))),
    K_HEQUAL_mean = mean(c_across(starts_with("K_HEQUAL"))),
    K_HREVDIS1_mean = mean(c_across(starts_with("K_HREVDIS1"))),
    K_EDISCRIM_mean = mean(c_across(starts_with("K_EDISCRIM"))),
    K_ERADEQ1_mean = mean(c_across(starts_with("K_ERADEQ1"))),
    K_ERADEQ2_mean = mean(c_across(starts_with("K_ERADEQ2")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

nkahanfinal <- data.frame(factor.scores(nkahanall[, 1:12], fit)$scores)

## Kahan: factor scores from 1st imputed dataset
```{r, echo=FALSE}

# extracting factor scores from mifa for 1st imputed dataset

@@

## Kahan: factor scores from second imputed dataset
```{r, echo=FALSE}

data_impk2 <- mice::complete(mice::mice(kahanall, 2, print = FALSE))

fct_scoresk2 <- data.frame(factor.scores(data_impk2[, 1:12], fit)$scores)

## Kahan: factor scores from third imputed dataset
```{r, echo=FALSE}

data_impk3 <- mice::complete(mice::mice(kahanall, 3, print = FALSE))

fct_scoresk3 <- data.frame(factor.scores(data_impk3[, 1:12], fit)$scores)

## Kahan: factor scores from fourth imputed dataset
```{r, echo=FALSE}

data_impk4 <- mice::complete(mice::mice(kahanall, 4, print = FALSE))

fct_scoresk4 <- data.frame(factor.scores(data_impk4[, 1:12], fit)$scores)

## Kahan: factor scores from fifth imputed dataset
```{r, echo=FALSE}

data_impk5 <- mice::complete(mice::mice(kahanall, 5, print = FALSE))

fct_scoresk5 <- data.frame(factor.scores(data_impk5[, 1:12], fit)$scores)

## are imputations plausible: Kahan scale - are values plausible ?

yes all value are whole numbers between 1 and 5

summary(mikahan)

str(data_imp)
names(mikahan)

@@

# Eco-pol scale: MAR condition and missing data pattern

ecopoln <- formice1 %>%
  dplyr::select(
    DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV,DEVOVERENV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State
  )

md.pattern(ecopoln) #the variables with missing values: PRIDENUCLEAR PROSPERNUCLEAR JOBSNUCLEAR HEALTHNUCLEAR BEAUTYNUCLEAR POLLUTENUCLEAR DISPLACENUCLEAR RELYNUCLEAR

mcar_test(data=ecopoln) # p values is less than 0.76 - the condition for MCAR is met

# dataset with missing variables to compare and test group comaprisons

MARecopol <- codedmodule2 %>%
          dplyr::select(c(DECISIONDECEN, DECISIONCEN, INDUSTRYSMALL, INDUSTRYLARGE,
    ECONOMYLOCAL, ECONOMYGLOBAL, ENVOVERDEV, OWNERPVT, OWNERPUB,
    OWNERREG, OWNERNOREG, WEALTHLIM, MECHANISATION,
    DISPLACENUCLEAR,  POLLUTENUCLEAR, HEALTHNUCLEAR, JOBSNUCLEAR, BEAUTYNUCLEAR,
    PRIDENUCLEAR, NPRIDENUCLEAR, DEVNUCLEAR, PROSPERNUCLEAR,
    RELYNUCLEAR,age, urban_rural, gender, caste, religion, State))

MARecopol$JOBSNUCLEAR_MAR <- MARecopol$JOBSNUCLEAR

MARecopol$PRIDENUCLEAR_MAR <- MARecopol$PRIDENUCLEAR

library(finalfit)

# JOBSNUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "JOBSNUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the JOBSNUCLEAR variable.")

# PRIDENUCLEAR
explanatory = c("age", "gender", "caste", "State", "urban_rural", "religion")
dependent = "PRIDENUCLEAR_MAR"
MARecopol %>% 
  missing_compare(dependent, explanatory) %>% 
    knitr::kable(row.names=FALSE, align = c("l", "l", "r", "r", "r"), 
        caption = "comparisons between values of responders (Not missing) and 
        non-responders (Missing) on the PRIDENUCLEAR variable.") 
```

## Mifa for new eco-pol value scale : Nuclear energy

miecopol <- mifa(data= ecopoln,
                cov_vars  = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 429,)

ecopolfit2 <- psych::fa(miecopol$cov_combined, nfactors = 2, rotate = "varimax")

print.psych(ecopolfit2, sort= TRUE, cut= 0.4)

@@

#Ecopol Factor scores: mean across all imputations

ecopolallscores <- mice::complete(mice::mice(ecopoln, m = 5, seed = 429, print = FALSE), "broad")

ecopolallscores <- ecopolallscores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

#str(ecopolallscores)

necopol <- ecopolallscores %>%
  rowwise() %>%
  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
         ECONOMYGLOBAL_mean = mean(c_across(starts_with("ECONOMYGLOBAL"))),
         WEALTHLIM_mean = mean(c_across(starts_with("WEALTHLIM"))),
         INDUSTRYLARGE_mean = mean(c_across(starts_with("INDUSTRYLARGE"))),
         DECISIONCEN_mean = mean(c_across(starts_with("DECISIONCEN"))),
         MECHANISATION_mean = mean(c_across(starts_with("MECHANISATION"))),
         OWNERNOREG_mean = mean(c_across(starts_with("OWNERNOREG"))),
         INDUSTRYSMALL_mean = mean(c_across(starts_with("INDUSTRYSMALL"))),
         DEVOVERENV_mean = mean(c_across(starts_with("DEVOVERENV"))),
         OWNERPVT_mean = mean(c_across(starts_with("OWNERPVT"))),
         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
         ENVOVERDEV_mean = mean(c_across(starts_with("ENVOVERDEV"))),
         OWNERPUB_mean = mean(c_across(starts_with("OWNERPUB"))),
         OWNERREG_mean = mean(c_across(starts_with("OWNERREG"))),
         DECISIONDECEN_mean = mean(c_across(starts_with("DECISIONDECEN"))),
         ECONOMYLOCAL_mean = mean(c_across(starts_with("ECONOMYLOCAL")))
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

necopolfinal <- data.frame(factor.scores(necopol[, 1:24], ecopolfit2)$scores)

# Eco-pol: Radar map

```{r, echo=FALSE}
library(ggplot2)
library(fmsb)

nrow(ecopolfit2$loadings)

# Extract the loadings
loadings_matrix4 <- ecopolfit2$loadings[1:24, ]

loadings_df2 <- as.data.frame(as.matrix(loadings_matrix4))

# Adding rownames to the dataframe as a new column
loadings_df2 <- loadings_df2 %>%
  rownames_to_column(var = "variable")

# Pivot to longer format first
long_loadings_df2 <- loadings_df2 %>%
  pivot_longer(cols = c(MR1, MR2), names_to = "Factors", values_to = "value")

# Pivot the longer format to wide format
wide_loadings_df2 <- long_loadings_df2 %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  mutate(Factors = case_when(
    Factors == "MR1" ~ "Nationalist Development (Ndevelop)",
    Factors == "MR2" ~ "People Centered Development (Pdevelop)",
    TRUE ~ Factors
  )) %>%
  column_to_rownames("Factors")

# Define the variable ranges: maximum and minimum
max_min2 <- data.frame(
  DEVNUCLEAR = c(0.8, -0.6), PROSPERNUCLEAR = c(0.8, -0.6), NPRIDENUCLEAR = c(0.8, -0.6), PRIDENUCLEAR = c(0.8, -0.6),     JOBSNUCLEAR = c(0.8, -0.6), ECONOMYGLOBAL = c(0.8, -0.6), WEALTHLIM = c(0.8, -0.6), INDUSTRYLARGE = c(0.8, -0.6),   DECISIONCEN = c(0.8, -0.6), MECHANISATION = c(0.8, -0.6), OWNERNOREG = c(0.8, -0.6), INDUSTRYSMALL = c(0.8, -0.6), DEVOVERENV = c(0.8, -0.6), OWNERPVT = c(0.8, -0.6), RELYNUCLEAR = c(0.8, -0.6), BEAUTYNUCLEAR = c(0.8, -0.6), HEALTHNUCLEAR = c(0.8, -0.6), POLLUTENUCLEAR = c(0.8, -0.6), DISPLACENUCLEAR = c(0.8, -0.6), DECISIONDECEN = c(0.8, -0.6),
ECONOMYLOCAL = c(0.8, -0.6), ENVOVERDEV = c(0.8, -0.6), OWNERPUB = c(0.8, -0.6), OWNERREG = c(0.8, -0.6)   
)
rownames(max_min2) <- c("Max", "Min")

# Assuming you have a dataframe 'exam_scores' with matching column names
# Bind the variable ranges to the data

radar4 <- rbind(max_min2, wide_loadings_df2) %>%
    rename(
      "National development(nuclear)" = "DEVNUCLEAR",
      "Local prosperity(nuclear)" = "PROSPERNUCLEAR",
      "National pride(nuclear)" = "NPRIDENUCLEAR",
      "Community pride(nuclear)" = "PRIDENUCLEAR",
      "Job opportunities(nuclear)" = "JOBSNUCLEAR",
      "Pro Globaleconomy" = "ECONOMYGLOBAL",
      "Limits on Wealth " = "WEALTHLIM",
      "Pro Large Industries" = "INDUSTRYLARGE",
      "Pro Centralisation" = "DECISIONCEN",
      "Anti Mechanisation of work" = "MECHANISATION",
      "Anti Regulations" = "OWNERNOREG",
      "Anti Large Industries " = "INDUSTRYSMALL",
      "Development over Environment" = "DEVOVERENV",
      "Pro Private ownership " = "OWNERPVT",
      "Reliance on government(nuclear)" = "RELYNUCLEAR",
      "Spoils Natural Beauty(nuclear)" = "BEAUTYNUCLEAR",
      "Health risk(nuclear)" = "HEALTHNUCLEAR",
      "Pollution risk(nuclear) " = "POLLUTENUCLEAR",
      "Displacement risk(nuclear)" = "DISPLACENUCLEAR",
      "Environment over Development" = "ENVOVERDEV",
      "Pro Public ownership" = "OWNERPUB",
      "Pro Regulations" = "OWNERREG",
      "Pro Decentralisation" = "DECISIONDECEN",
      "Pro Localeconomy" = "ECONOMYLOCAL",
    )

```{r, echo=FALSE, fig.width=15, fig.height=7, out.width='70', out.height='70'}
library(fmsb)

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.7), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "black", cglty = 1, cglwd = 2,
    # Customize the axis
    axislabcol = "black", cexc = 1.5, # Increase label size for axis
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
    seg = 7, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 4,
    ...
  )
}

# Reduce plot margin using par()
op <- par(mar = c(7, 3, 3, 3))
# Create the radar charts
create_beautiful_radarchart(
  data = radar4, caxislabels = c(-0.6, -0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8),
  color = c( "#F97D09","#00AFBB"),
  vlcex = 1.1
)

# Add an horizontal legend
legend(
  x = "bottomright", legend = rownames(radar4[-c(1,2),]), horiz = TRUE,
  bty = "n", pch = 20 , col = c("#F97D09","#00AFBB"),
  text.col = "black", cex = 1.5, pt.cex = 3,
  inset = c(0, 0)
  )
par(op)

# Extracting factors from first imputed dataset

@@

fct_scores2 <- data.frame(factor.scores(data_imp2[, 1:24], ecopolfit2)$scores)

@@

##  eco-pol scale : Factor scores from 2nd imputation
```{r, echo=FALSE}

data_impe2 <- mice::complete(mice::mice(ecopoln, 2, print = FALSE))

fct_scorese2 <- data.frame(factor.scores(data_impe2[, 1:24], ecopolfit2)$scores)

##  eco-pol scale : Factor scores from 3rd imputation
```{r, echo=FALSE}

data_impe3 <- mice::complete(mice::mice(ecopoln, 3, print = FALSE))

fct_scorese3 <- data.frame(factor.scores(data_impe3[, 1:24], ecopolfit2)$scores)

##  eco-pol scale : Factor scores from 4th imputation
```{r, echo=FALSE}

data_impe4 <- mice::complete(mice::mice(ecopoln, 4, print = FALSE))

fct_scorese4 <- data.frame(factor.scores(data_impe4[, 1:24], ecopolfit2)$scores)

##  eco-pol scale : Factor scores from 5th imputation
```{r, echo=FALSE}

data_impe5 <- mice::complete(mice::mice(ecopoln, 5, print = FALSE))

fct_scorese5 <- data.frame(factor.scores(data_impe5[, 1:24], ecopolfit2)$scores)

## Are imputations plausible : Eco-pol scale

yes, imputations are pluasible- all natural numbers between 1 and 5

@@

# Checking consistency of LM coefficients across 5 imputed datasets 
coefficients and LMs are fairly consistent

## Binding datasets: 1st imputation

```{r, echo = FALSE}

# binding the imputed  factor analysis scores for kahan scale and eco-pol value scale to the larger dataset codedmodule2

ecopolnuclear <- fct_scores2 %>%
  rename(Ndevelop = MR1, Pdevelop = MR2)

kahannuclear <- fct_scores%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

allformice<- cbind(formice1,ecopolnuclear, kahannuclear)

@@

## State Ns before MIFA

```{r, echo=FALSE}
Statenacheck1 <- allformice%>%
  na.omit()%>%
  dplyr::select(State)

summary(Statenacheck1)
```

# Allformice: Do imputations merge ?

# Initialize the mice process to create the predictor matrix
#ini <- mice(allformice, maxit = 0, pri = FALSE)

# Extract the predictor matrix from the initialized object
#pred <- ini$predictorMatrix

# Set the columns for "Uppercaste", "Male", "Hindu", and "Age" to 0
#pred[, "Uppercaste"] <- 0
#pred[, "Male"] <- 0
#pred[, "Hindu"] <- 0
#pred[, "Age"] <- 0
#pred[, "Ndevelop"] <- 0
#pred[, "Pdevelop"] <- 0
#pred[, "Hierarchy_Egalitarian"] <- 0
#pred[, "Communitarian"] <- 0
# Identify columns that start with "K_" and set them to 0
#k_columns <- grep("^K_", colnames(formice1))
#pred[, k_columns] <- 0

# Perform the mice imputation with the updated predictor matrix
#allformice.imp <- mice(allformice, m = 5, maxit = 10, predictorMatrix = pred, seed = 430, print = TRUE)

#summary(allformice.imp)
#allformice.imp$chainMean

#plot(allformice.imp)

@@

## State Ns after MIFA on two scales

nuclear_missing <- allformice %>% dplyr::select(Risky_Nuclear,Uppercaste, Male, Hindu, urban_rural, Age, State)%>%
  na.omit()

summary(nuclear_missing)

@@

## LMs with 1st imputed datasets from FAs

nuclearIVmice <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice)

nuclearIVmice2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice)

nuclearIVmice3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice)

summary(nuclearIVmice)
summary(nuclearIVmice2)
summary(nuclearIVmice3)

## binding dataset - 2nd imputation

ecopolnuclear2 <- fct_scorese2 %>%
  rename(Ndevelop = MR1, Pdevelop = MR2)

kahannuclear2 <- fct_scoresk2%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

allformice2<- cbind(formice1,ecopolnuclear2, kahannuclear2)

## LMs with second imputation 
```{r, echo=FALSE}

nuclearIVmiceimp2 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice2)

nuclearIVmiceimp22 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice2)

nuclearIVmiceimp23 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice2)

summary(nuclearIVmiceimp2)
summary(nuclearIVmiceimp22)
summary(nuclearIVmiceimp23)

## binding dataset - 3rd imputation

ecopolnuclear3 <- fct_scorese3 %>%
  rename(Ndevelop = MR1, Pdevelop = MR2)

kahannuclear3 <- fct_scoresk3%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

allformice3<- cbind(formice1,ecopolnuclear3, kahannuclear3)

## LMs with third imputation 
```{r, echo=FALSE}

nuclearIVmiceimp3 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice3)

nuclearIVmiceimp32 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice3)

nuclearIVmiceimp33 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian + Pdevelop + Ndevelop, data = allformice3)

summary(nuclearIVmiceimp3)
summary(nuclearIVmiceimp32)
summary(nuclearIVmiceimp33)

## binding dataset - 4th imputation

ecopolnuclear4 <- fct_scorese4 %>%
  rename(Ndevelop = MR1, Pdevelop = MR2)

kahannuclear4 <- fct_scoresk4%>%
  rename(Hierarchy_Egalitarian = MR1, Communitarian = MR2)

allformice4<- cbind(formice1, ecopolnuclear4, kahannuclear4)

## LMs with fourth imputation 
```{r, echo=FALSE}

nuclearIVmiceimp4 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State, data = allformice4)

nuclearIVmiceimp24 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + urban_rural + Age + State + Communitarian + Hierarchy_Egalitarian, data = allformice4)
